Appendix to 'Detecting social information in a dense database of infants’ natural

### 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd
replaced linear regression tables with quadratic reg tables

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lsr) 
library(stringr)
library(lmerTest)
library(here)
theme_set(theme_few())
```

@@

Finally, we analyzed how these two sources of social information co-occurred, finding that faces/hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}). 
To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. 
As shown in Figure \ref{fig:faceHandContingency}, we found that all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently. 
That is, generally speaking when a face was present, a hand also tended to be present.

```{r eval=FALSE}
summary_by_age_days <- all_vid_data %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(num_faces), 
            num_faces_center = sum(num_faces_center), 
            num_hands = sum(num_hands), 
            num_hands_center = sum(num_hands_center), 
            num_detect = sum(num_frames)) %>%
  mutate(prop_faces = num_faces / num_detect, 
         prop_hands = num_hands / num_detect,
         prop_faces_center = num_faces_center / num_detect, 
          prop_hands_center = num_hands_center / num_detect)

@@

```{r eval=FALSE}
# run lmer models -- faces over age
faces_model_full_age_out = summary(lmer(prop_faces_center ~ age_scale + (1 | child_id), data = summary_by_age_days))

# hands over age
hands_model_full_age_out = summary(lmer(prop_hands_center ~ age_scale + (1 | child_id), data = summary_by_age_days))

# explicit modeling of faces vs. hands and interaction with age
# main effect of ages and regions; no interaction.
diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = long_summary_by_age_days))
```

```{r eval=FALSE}
xtable(faces_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.")

xtable(hands_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of hands seen by infants n the center FOV.")
```

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.098 & 0.010 & 1.956 & 9.386 & 0.012 \\ 
  Age & -0.001 & 0.000 & 430.976 & -3.150 & 0.002 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.161 & 0.009 & 1.881 & 18.046 & 0.004 \\ 
  Age & -0.001 & 0.001 & 428.651 & -1.680 & 0.094 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants n the center FOV.} 
\end{table}

@@

```{r}
x_pos_summary = summary(lmer(data=CV_faces %>% filter(position == 'Face X Position'), CV ~ scale(age_day_bin) + scale(num_detect) + (1|child_id)))

>>>>

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(lsr) 
library(stringr)
library(lmerTest)
library(here)
library(papaja)
theme_set(theme_few())
```

@@

Finally, we analyzed how these two sources of social information co-occurred, finding that faces/hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}). 
To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. 
We found that all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently. 
That is, generally speaking when a face was present, a hand also tended to be present (see also Figure \ref{fig:faceHandContingency}).

```{r eval=T}
summary_by_age_days <- all_vid_data %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(num_faces), 
            num_faces_center = sum(num_faces_center), 
            num_hands = sum(num_hands), 
            num_hands_center = sum(num_hands_center), 
            num_detect = sum(num_frames)) %>%
  mutate(prop_faces = num_faces / num_detect, 
         prop_hands = num_hands / num_detect,
         prop_faces_center = num_faces_center / num_detect, 
          prop_hands_center = num_hands_center / num_detect)

@@

```{r eval=T, include=F, echo=F}
# run lmer models -- faces over age
faces_model1 <- lmer(prop_faces_center ~ age_scale + (1 | child_id), data = summary_by_age_days)
faces_model_full_age_out = summary(faces_model1)
# # singular:
#faces_model2 = summary(lmer(prop_faces_center ~ poly(age_scale, 2) + (poly(age_scale, 2) | child_id), 
#                            data = summary_by_age_days))
faces_model2 <- lmer(prop_faces_center ~ poly(age_scale, 2) + (1 | child_id), 
                            data = summary_by_age_days)
faces_comparison <- anova(faces_model1, faces_model2) # chisq 7.17 p = 0.007407 ** - complex model preferred
faces_out <- summary(faces_model2) # poly(age_scale, 2)1 -.20 **, poly(age_scale, 2)2 -.16**

# hands over age
hands_model1 <- lmer(prop_hands_center ~ age_scale + (1 | child_id), data = summary_by_age_days)
hands_model_full_age_out = summary(hands_model1)
hands_model2 <- lmer(prop_hands_center ~ poly(age_scale, 2) + (1 | child_id), 
                            data = summary_by_age_days)
hands_comparison <- anova(hands_model1, hands_model2) # chisq = 17.11, p<.001 - complex model preferred

hands_out <- summary(hands_model2) # poly(age_scale, 2)1  -0.14, p=.06, poly(age_scale, 2)2  -0.32, p<.001

# explicit modeling of faces vs. hands and interaction with age
# main effect of ages and regions; no interaction.
diff_model1 <- lmer(prop ~ region*age_scale + (1 | child_id), data = long_summary_by_age_days)
diff_model_full_age_out = summary(diff_model1)
diff_model2 <- lmer(prop ~ region*poly(age_scale, 2) + (1 | child_id), data = long_summary_by_age_days)
diff_comparison <- anova(diff_model1, diff_model2) # chisq = 23.66, p<.001 - complex model preferred

diff_out <- summary(diff_model2) 
# regionprop_hands .04***, poly(age_scale, 2)1 -.42**, poly(age_scale, 2)2 -.29*, marginal hand*poly(age_scale, 2)2
```

```{r faces-regression-table}
faces_tab <- faces_out$coefficients
rownames(faces_tab)[2] = "Age"
rownames(faces_tab)[3] = "Age**2"
apa_table(faces_tab, digits=3,
           caption = "Coefficients from a mixed-effects regression predicting the proportion of faces seen by infants in the center FOV.")
```

```{r hands-regression-table}
hands_tab <- round(hands_out$coefficients, 3)
rownames(hands_tab)[2] = "Age"
rownames(hands_tab)[3] = "Age**2"
hands_tab[3,5] = "<.001"
apa_table(hands_tab, 
           caption = "Coefficients from a mixed-effects regression predicting the proportion of hands seen by infants in the center FOV.")
```

```{r linear-regression-tables, eval=FALSE, include=F}
# old -- now want the above poly models
xtable(faces_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.")

xtable(hands_model_full_age_out$coefficients, digits=c(4,3,3,3,3,3),"Model coefficients from a linear mixed model predicting the proportion of hands seen by infants in the center FOV.")
```

<!-- old linear regression tables
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.098 & 0.010 & 1.956 & 9.386 & 0.012 \\ 
  Age & -0.001 & 0.000 & 430.976 & -3.150 & 0.002 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.161 & 0.009 & 1.881 & 18.046 & 0.004 \\ 
  Age & -0.001 & 0.001 & 428.651 & -1.680 & 0.094 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants n the center FOV.} 
\end{table}
-->

@@

```{r, include=F}
x_pos_summary = summary(lmer(data=CV_faces %>% filter(position == 'Face X Position'), CV ~ scale(age_day_bin) + scale(num_detect) + (1|child_id)))
